---
title: "Milestone 4"
author: "Hansang Park"
date: "11/19/2021"
output: html_document
---
## Loading libraries, database, and setup for visualization
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(dplyr)

#Import statements - I will use df10 which is cleaned from project.Rmd file
data <- df10 %>%
  rename(County=name)%>%
  rename(Mean_Vaccination_Rate_Percentage=mean_vx_prct)%>%
  rename(Population_2012=pop2012)%>%
  rename(Median_Age=med_age)
view(data)
```

## Milestone 4
Visualizations
Please submit an Rmd and either a knit PDF or html file via github with the following:
1.	Three or more visualizations 
o	One print quality table as requested in scenario
o	One print quality plot or chart as requested in scenario
o	One additional print quality table or plot of your choice (can support the requested data in the scenario, or answer a different question using the same data sources)
2.	For each visual, include
o	Code used to generate visual
o	Legend
o	2-3 sentence interpretation 
o	NOTE: please make sure visual can stand-alone, meaning it includes enough information in title, legend, and footnote so that a person who sees only the visualization could understand what is being presented
3.	PDF that is professionally prepared for presentation
o	Each part of the milestone is clearly on one page (use \newpage to push to a new page)
o	Only the necessary information is outputted (e.g., suppressing entire data frame outputs)
o	Use of headers and sub headers to create an organized document

#### 1. Visualization 1 - table
Include code used to generate visual, legend, 2-3 sentence interpretation. 
Please make sure visual can stand-alone, meaning it includes enough information in title, legend, and footnote so that a person who sees only the visualization could understand what is being presented.

Suggestion: Create joined table showing county, median age, and percentages of vaccinated persons.

```{r}


```

\newpage

#### 2. Visualization 2 - plot or chart

Include code used to generate visual, legend, 2-3 sentence interpretation. 
Please make sure visual can stand-alone, meaning it includes enough information in title, legend, and footnote so that a person who sees only the visualization could understand what is being presented.

Suggestion: Create plot showing percentages of vaccinated persons by county.

```{r}

```

\newpage

#### 3. Visualization 3 - One additional print quality table or plot of your choice
  Can support the requested data in the scenario, or answer a different question using the same data sources. 
  
  Include code used to generate visual, legend, 2-3 sentence interpretation. 
Please make sure visual can stand-alone, meaning it includes enough information in title, legend, and footnote so that a person who sees only the visualization could understand what is being presented.

Suggestion: Create plot showing percentages of vaccinated persons by county's median age.

```{r}

```

  
\newpage

#### 4. PDF professionally prepared for presentation

o	Each part of the milestone is clearly on one page (use \newpage to push to a new page)
o	Only the necessary information is outputted (e.g., suppressing entire data frame outputs)
o	Use of headers and sub headers to create an organized document

What evidence if any exists of a strong correlative relationship, and if so in what direction?

```{r}

```

\newpage